Chord: A Versatile Platform for Program Analysis

### 2011-03-14 main/doc/properties.tex
more documentation

A property can be passed to Chord in any of several ways.
The reason for providing multiple ways is to provide users shorthand ways for defining properties
once and for all for a particular input Java program, or even once and for all across all Chord runs. 
The following are the different ways by which a property can be passed to Chord in decreasing order of precedence:
\begin{enumerate}
\item
On the command-line via the \code{-D<key>=<value>} format.

@@

Typical usage of this option is by running the following command in
the \code{main/} directory of Chord's installation:
\begin{verbatim}
    prompt> ant -D<key1>=<value1> ... -D<keyN>=<valueN> run
\end{verbatim}

\item
Via the file specified by property \code{chord.props.file}.

@@

\item
Via file \code{main/chord.properties}.

Use this option to specify once and for all properties you would like to hold in every run of Chord
(e.g., property \code{chord.max.heap} specifying the maximum runtime heap size to be used by the
JVM running Chord).
\end{enumerate}

@@

This section describes basic properties of the given Java program, such as
its main class, the location(s) of its class files and Java source
files, and command-line arguments to be used to run the program.
\\[10pt]

\code{chord.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution.  This is
usually the top-level directory of the given program. \\
{\bf Default value:} current working directory
\end{quote}

@@

\code{chord.main.class}
\begin{quote}
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the given program (e.g., \code{com.example.Main}).
\end{quote}

\code{chord.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath of the given program.  It does not need to include
boot classes (i.e., classes in \code{[sun.boot.class.path]}) or
standard extensions (i.e., classes in {\tt .jar} files in directory
\code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.src.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Java source path of the given program. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Chord analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by program analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.
\end{quote}

\code{chord.run.ids}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the given program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

\code{chord.args.<id>}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the given program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis.
\end{quote}

\code{chord.runtime.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the given program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when Chord executes the given program, namely, when it is asked to compute the program scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to execute a dynamic program analysis. 
\end{quote}

@@

This section describes properties that specify how the analysis scope of the given program is computed.
See Chapter \ref{chap:computing-scope} for more details.
\\[10pt]

\code{chord.scope.kind}
\begin{quote}
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute program scope.  The choices are {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta}
\end{quote}

@@

\code{chord.ch.kind}
\begin{quote}
{\bf Type:} {\tt [static|dynamic]} \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the given program is executed and classes not loaded by the JVM while running the program are excluded while building the class hierarchy. \\
{\bf Default value:} {\tt static} \\
{\bf Note:} This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this scope computing algorithm queries the class hierarchy. 
\end{quote}

\code{chord.ssa}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Do SSA transformation for all methods deemed reachable by the algorithm used to compute program scope. \\
{\bf Default value:} {\tt true}
\end{quote}

@@

\code{chord.std.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of all programs to be analyzed, e.g., classes in the JDK standard library. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.ext.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes whose declared methods must be treated as no-ops.  Conventionally, this property is used to specify classes to be excluded from the scope of specific programs to be analyzed. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes whose declared methods must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{quote}

\code{chord.std.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages inside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,javax.,sun.,com.sun.,com.ibm.,} \code{org.apache.harmony."}
\end{quote}

\code{chord.ext.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages outside the standard library to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of prefixes of names of classes and packages to be excluded by program analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.std.check.exclude],[chord.ext.check.exclude]"}
\end{quote}

@@

\code{chord.build.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute the scope of the given program using the algorithm specified by properties \code{chord.scope.kind} and \code{chord.reuse.scope}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The program scope is computed regardless of the value of this property if another task (e.g., a program analysis specified via property \code{chord.run.analyses}) demands it by calling method \code{chord.program.Program.g()}. 
\end{quote}

\code{chord.run.analyses}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program analyses to be run in order. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} If the analysis is written in Java, its name is specified via statement {\tt name=<...>} in its {\tt @Chord} annotation, and is the name of the class itself if this statement is missing.  If the analysis is written in Datalog, its name is specified via a line of the form ``{\tt \# name=<...>}", and is the absolute location of the file itself if this line is missing. 
\end{quote}

\code{chord.print.methods}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of methods in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Specify each method in format \code{<mname>:<mdesc>@<cname>} where {\tt <mname>} is the method's name, {\tt <mdesc>} is the method's descriptor, and {\tt <cname>} is the name of the method's declaring class. In {\tt <cname>}, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\code{chord.print.classes}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of classes in scope whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} In class names, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

@@

\code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., billions) of tuples, resulting in voluminous output when printed to a file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in Chord's {\tt main/} directory). 
\end{quote}

\code{chord.print.project}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all tasks and targets defined by program analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}.  \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.print.results}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print the results of program analyses in HTML.  Interpretation of this property is analysis-specific.  \\
{\bf Default value:} {\tt true}
\end{quote}

\code{chord.verbose}
\begin{quote}
{\bf Type:} int in the range [0..6]  \\
{\bf Description:} Control the verbosity of logging during Chord's execution.  \\
{\bf Default value:} {\tt 2}
\end{quote}

@@

This section describes properties regarding program analyses executed by Chord.
\\[10pt]

@@

\code{chord.std.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.ext.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath containing program analyses written in Java (i.e., {\tt @Chord}-annotated classes).  \\
{\bf Default value:} \code{[chord.main.dir]/classes/}
\end{quote}

\code{chord.std.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.ext.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.dlog.analysis.path}
\begin{quote}
{\bf Type:} path  \\
{\bf Description:} Path of directories containing program analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.main.dir]/src/}
\end{quote}

@@

This section describes properties regarding execution of instrumented programs for dynamic analyses.
\\[10pt]

% TODO: mention chord.scope.exclude* here
\code{chord.use.jvmti}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

@@

\code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the event file used by a multi-JVM dynamic analysis. \\
{\bf Default value:} {\tt 4096}
\end{quote}

\code{chord.dynamic.haltonerr}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether or not to terminate Chord if the given program terminates abnormally during dynamic analysis. \\
{\bf Default value:} true
\end{quote}

@@

TODO
\\[10pt]

\code{chord.reuse.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute program scope using the information in files specified by properties \code{chord.methods.file} and \code{chord.reflect.file}. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. 
\end{quote}

\code{chord.reuse.rels}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Construct program relations from BDDs stored on disk (from a previous run of Chord) whenever possible instead of re-computing them. \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.reuse.traces}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Reuse dynamic traces computed by a previous run of Chord if they exist.  Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}. \\
{\bf Default value:} {\tt false}
\end{quote}

@@

TODO
\\[10pt]

\code{java.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{user.dir}
\begin{quote}
{\bf Type:} location
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.max.heap}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running Chord. \\
{\bf Default value:} {\tt 1024m}
\end{quote}

\code{chord.max.stack}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum thread stack size of JVM running Chord. \\
{\bf Default value:} {\tt 32m}
\end{quote}

\code{chord.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to JVM running Chord. \\
{\bf Default value:} \code{"-showversion} \code{-ea} \code{-Xmx[chord.max.heap]} \code{-Xss[chord.max.stack]"}
\end{quote}

@@

TODO
\\[10pt]

\code{chord.use.buddy}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} TODO \\
{\bf Default value:} TODO
\end{quote}

\code{chord.bddbddb.max.heap}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum memory size of JVM running Datalog solver bddbddb. \\
{\bf Default value:} {\tt 1024m} \\
{\bf Note:}  Each program analysis written in Datalog is run in a separate JVM.  This is primarily because there may be multiple invocations of bddbddb in a single run of Chord and it is difficult to reset the global state of bddbddb on each invocation. 
\end{quote}

@@

This section describes properties specifying the names of files and directories output by Chord.
Most users will not want to alter the default values of these properties.
\\[10pt]

@@

\code{chord.bddbddb.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory used by the Datalog solver bddbddb as its input/output directory (namely, for program domain files {\tt *.dom} and {\tt *.map}, and program relation files {\tt *.bdd}). \\
{\bf Default value:} \code{[chord.out.dir]/bddbddb/}
\end{quote}

\code{chord.boot.classes.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory from/to which instrumented JDK classes used by the given program are read/written by dynamic program analyses. \\
{\bf Default value:} \code{[chord.out.dir]/boot_classes/}
\end{quote}

\code{chord.user.classes.dir}
\begin{quote}
{\bf Type:} location  \\
{\bf Description:} Absolute location of the directory from/to which instrumented non-JDK classes of the given program are read/written by dynamic program analyses. \\
{\bf Default value:} \code{[chord.out.dir]/user_classes/}
\end{quote}

\code{chord.instr.scheme.file}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the file specifying the kind and format of events in dynamic trace files. \\
{\bf Default value:} \code{[chord.out.dir]/scheme.ser}
\end{quote}

\code{chord.trace.file}
\begin{quote}
{\bf Type:} location  \\
{\bf Description:} Absolute location of the dynamic trace file.  \\
{\bf Default value:} \code{[chord.out.dir]/trace} \\
{\bf Note:} Suffix \code{_full_verN.txt} or \code{_pipe_verN.txt} is appended to the name of the file, depending upon whether it is a regular file or a POSIX pipe, respectively, where {\tt N} is the version of the file (multiple versions are maintained if the trace is transformed by filters defined by the dynamic analysis; 0 is the final version).  If \code{chord.reuse.traces} is set to {\tt true}, then \code{_full_verN_runM.txt} is appended to the name of the file, where {\tt M} is the run ID. 
\end{quote}

>>>>

A property can be passed to Chord in any of several ways.
The reason for providing multiple ways is to provide users shorthand ways for defining properties
once and for all for a particular input Java program, or even once and for all across all Chord runs. 
The following are the different ways by which a property can be passed to Chord in decreasing order of precedence:

\begin{enumerate}
\item

On the command-line via the \code{-D<key>=<value>} format.

@@

Typical usage of this option is by running the following command in Chord's \code{main/} directory:
\begin{verbatim}
    prompt> ant -D<key1>=<value1> ... -D<keyN>=<valueN> run
\end{verbatim}

\item

Via the file specified by property \code{chord.props.file}.

@@

\item

Via file \code{main/chord.properties}.

Use this option to specify once and for all properties you would like to hold in every run of Chord
(e.g., property \code{chord.max.heap} specifying the maximum heap memory size to be used by the
JVM running Chord).
\end{enumerate}

@@

This section describes properties of the Java program to be analyzed, such as
its main class, the location(s) of its class files and Java source
files, and command-line arguments to be used to run the program.
\\[10pt]

\code{chord.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Working directory during Chord's execution.  This is
usually the top-level directory of the input Java program. \\
{\bf Default value:} current working directory
\end{quote}

@@

\code{chord.main.class}
\begin{quote}
{\bf Type:} class \\
{\bf Description:} Fully-qualified name of the main class of the input Java program (e.g., \code{com.example.Main}).
\end{quote}

\code{chord.class.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Classpath of the input Java program.  It does not need to include
boot classes (i.e., classes in \code{[sun.boot.class.path]}) or
standard extensions (i.e., classes in jar files in directory \code{[java.home]/lib/ext/}). \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.src.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Source path of the input Java program. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Chord analyzes only Java bytecode, not Java source code.  This property is used only by the task of converting Java source files into HTML files by analyses that need to present their analysis results at the Java source code level (by calling method \code{chord.program.Program.g().HTMLizeJavaSrcFiles())}.
\end{quote}

\code{chord.run.ids}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} List of IDs to identify runs of the input Java program. \\
{\bf Default value:} {\tt 0} \\
{\bf Note:} This property is used only when Chord runs the input Java program, namely, when it is asked to compute the analysis scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to run a dynamic analysis. 
\end{quote}

\code{chord.args.<id>}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Command-line arguments string to be used for the input Java program in the run having ID {\tt <id>}. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This property is used only when Chord runs the input Java program, namely, when it is asked to compute the analysis scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to run a dynamic analysis.
\end{quote}

\code{chord.runtime.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to JVM which runs the input Java program. \\
{\bf Default value:} {\tt "-ea -Xmx1024m"} \\
{\bf Note:} This property is used only when Chord runs the input Java program, namely, when it is asked to compute the analysis scope dynamically (i.e., when \code{[chord.scope.kind]=dynamic}) or when it is asked to run a dynamic analysis. 
\end{quote}

@@

This section describes properties that specify how the analysis scope of the input Java program is computed.
See Chapter \ref{chap:computing-scope} for more details.
\\[10pt]

\code{chord.scope.kind}
\begin{quote}
{\bf Type:} {\tt [dynamic|rta|cha]} \\
{\bf Description:} Algorithm to compute analysis scope.  The choices are {\tt dynamic} (dynamic analysis), {\tt rta} (Rapid Type Analysis), and {\tt cha} (Class Hierarchy Analysis). \\
{\bf Default value:} {\tt rta} \\
{\bf Note:} This property is ignored if property \code{chord.reuse.scope} is set to {\tt true} and the files specified by properties \code{chord.methods.file} and \code{chord.reflect.file} exist. 
\end{quote}

@@

\code{chord.ch.kind}
\begin{quote}
{\bf Type:} {\tt [static|dynamic]} \\
{\bf Description:} Algorithm to build the class hierarchy.  If it is {\tt dynamic}, then the input Java program is executed
and classes not loaded by the JVM while running the program are excluded while building the class hierarchy. \\
{\bf Default value:} {\tt static} \\
{\bf Note:} This property is relevant only if \code{chord.scope.kind} is {\tt cha} since only this
scope computing algorithm queries the class hierarchy. 
\end{quote}

\code{chord.ssa}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Do SSA (Static Single Assignment) transformation of the bodies of all methods deemed reachable by the algorithm used to compute analysis scope. \\
{\bf Default value:} {\tt true}
\end{quote}

@@

\code{chord.std.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes, typically inside the JDK standard library, whose methods must be treated as no-ops. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.ext.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes, typically outside the JDK standard library, whose methods must be treated as no-ops. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.scope.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes whose methods must be treated as no-ops. \\
{\bf Default value:} \code{"[chord.std.scope.exclude],[chord.ext.scope.exclude]"}
\end{quote}

\code{chord.std.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes, typically inside the JDK standard library, to be excluded by analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"java.,javax.,sun.,com.sun.,com.ibm.,} \code{org.apache.harmony."}
\end{quote}

\code{chord.ext.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Partial list of prefixes of names of classes, typically outside the JDK standard library, to be excluded by analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.check.exclude}
\begin{quote}
{\bf Type:} string list \\
{\bf Description:} Complete list of prefixes of names of classes to be excluded by analyses.  Interpretation of this property is analysis-specific. \\
{\bf Default value:} \code{"[chord.std.check.exclude],[chord.ext.check.exclude]"}
\end{quote}

@@

\code{chord.build.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute the analysis scope of the input Java program using the algorithm. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} The analysis scope is computed regardless of the value of this property if another task (e.g., an analysis specified via property \code{chord.run.analyses}) demands it.
\end{quote}

\code{chord.run.analyses}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of analyses to be run in order. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} If the analysis is written in Java, its name is specified via statement {\tt name=<...>} in its {\tt @Chord} annotation.  If the analysis is written in Datalog, its name is specified via a line of the form ``{\tt \# name=<...>}".
\end{quote}

\code{chord.print.methods}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of methods whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} Specify each method in format \code{<mname>:<mdesc>@<cname>} where {\tt <mname>} is the method's name, {\tt <mdesc>} is the method's descriptor, and {\tt <cname>} is the name of the method's declaring class. In {\tt <cname>}, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

\code{chord.print.classes}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of classes whose intermediate representation to print to standard output. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} In class names, use `.' instead of `/', and use {\tt \#} instead of the dollar character. 
\end{quote}

@@

\code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<...>.txt} where {\tt <...>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain a large number (e.g., millions) of tuples, resulting in voluminous output when printed in explicit form to a text file.  See Section \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug} target provided in file {\tt build.xml} in Chord's \code{main/} directory).
\end{quote}

\code{chord.print.project}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Create files \code{targets_sortby_name.html}, \code{targets_sortby_kind.html}, and \code{targets_sortby_producers.html} in directory \code{[chord.out.dir]}, publishing all tasks and targets defined by analyses in paths \code{[chord.java.analysis.path]} and \code{[chord.dlog.analysis.path]}.  \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.print.results}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Print the results of analyses in HTML.  Interpretation of this property is analysis-specific.  \\
{\bf Default value:} {\tt true}
\end{quote}

\code{chord.verbose}
\begin{quote}
{\bf Type:} int in the range [0..5]  \\
{\bf Description:} Control the verbosity of messages during Chord's execution.  \\
{\bf Default value:} {\tt 1}
\end{quote}

@@

This section describes properties regarding analyses executed by Chord.
\\[10pt]

@@

\code{chord.std.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Partial classpath of analyses written in Java (i.e., {\tt @Chord}-annotated classes).
Conventionally, it includes all such analyses that are predefined in Chord.  \\
{\bf Default value:} The absolute path of file \code{chord.jar}
\end{quote}

\code{chord.ext.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Partial classpath of analyses written in Java (i.e., {\tt @Chord}-annotated classes).
Conventionally, it includes all such external analyses that users want to run. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.java.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Complete classpath of analyses written in Java (i.e., {\tt @Chord}-annotated classes). \\
{\bf Default value:} \code{[chord.std.java.analysis.path]:[chord.ext.java.analysis.path]}
\end{quote}

\code{chord.std.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Partial classpath of analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}).
Conventionally, it includes all such analyses that are predefined in Chord.  \\
{\bf Default value:} The absolute path of file \code{chord.jar}
\end{quote}

\code{chord.ext.dlog.analysis.path}
\begin{quote}
{\bf Type:} path \\
{\bf Description:} Partial classpath of analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}).
Conventionally, it includes all such external analyses that users want to run. \\
{\bf Default value:} {\tt ""}
\end{quote}

\code{chord.dlog.analysis.path}
\begin{quote}
{\bf Type:} path  \\
{\bf Description:} Complete classpath of analyses written in Datalog (i.e., files with suffix {\tt .dlog} or {\tt .datalog}). \\
{\bf Default value:} \code{[chord.std.dlog.analysis.path]:[chord.ext.dlog.analysis.path]}
\end{quote}

@@

This section describes properties regarding bytecode instrumentation and dynamic analysis.
\\[10pt]

% TODO: mention chord.scope.exclude* here
\code{chord.use.jvmti}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether the JVMTI-based bytecode instrumentation agent from \code{main/agent/} must be used for running dynamic analyses. \\
{\bf Default value:} \code{false}
\end{quote}

@@

\code{chord.trace.block.size}
\begin{quote}
{\bf Type:} int \\
{\bf Description:} Number of bytes to read/write in a single operation from/to the event trace file in a multi-JVM dynamic analysis. \\
{\bf Default value:} {\tt 4096}
\end{quote}

\code{chord.dynamic.haltonerr}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether to terminate Chord if the input Java program terminates abnormally during dynamic analysis. \\
{\bf Default value:} true
\end{quote}

@@

This section describes properties that specify what must be reused by Chord, if available, from previous runs instead of recomputing.
\\[10pt]

\code{chord.reuse.scope}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Compute analysis scope using the information in files specified by properties \code{chord.methods.file} and \code{chord.reflect.file}, if both of those files exist. \\
{\bf Default value:} {\tt false} \\
{\bf Note:} Property \code{chord.scope.kind} is ignored if this property is set to {\tt true} and the two files exist. 
\end{quote}

\code{chord.reuse.rels}
\begin{quote}
{\bf Type:} bool  \\
{\bf Description:} Load each desired program relation named \code{<name>} from the BDD stored in file \code{[chord.bddbddb.work.dir]/<name>.bdd}, if the file exists. \\
{\bf Default value:} {\tt false}
\end{quote}

\code{chord.reuse.traces}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Reuse event traces stored in file(s) \code{chord.trace.file]_full_ver0_runM.txt} for dynamic analysis, if those files exist,
where \code{M} ranges over run IDs specified by property \code{chord.run.ids}.
Property \code{chord.trace.kind} must be set to {\tt full} if this property is set to {\tt true}. \\
{\bf Default value:} {\tt false}
\end{quote}

@@

This section describes properties regarding the JVM that runs Chord.
\\[10pt]

\code{chord.max.heap}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum heap memory size of the JVM running Chord. \\
{\bf Default value:} {\tt 1024m}
\end{quote}

\code{chord.max.stack}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum thread stack size of the JVM running Chord. \\
{\bf Default value:} {\tt 32m}
\end{quote}

\code{chord.jvmargs}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Arguments to the JVM running Chord. \\
{\bf Default value:} \code{"-showversion} \code{-ea} \code{-Xmx[chord.max.heap]} \code{-Xss[chord.max.stack]"}
\end{quote}

@@

This section describes properties concerning BDD-based Datalog solver bddbddb that is used by Chord to run analyses written in Datalog.
\\[10pt]

\code{chord.use.buddy}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether BDD library BuDDy from \code{main/bdd/} must be used by bddbddb. \\
{\bf Default value:} \code{false}
\end{quote}

\code{chord.bddbddb.max.heap}
\begin{quote}
{\bf Type:} string \\
{\bf Description:} Maximum heap memory size of JVM running bddbddb. \\
{\bf Default value:} {\tt 1024m} \\
{\bf Note:} bddbddb is invoked in a separate JVM for each analysis written in Datalog that is executed.
This is primarily because multiple Datalog analyses may be executed in a single run of Chord,
resulting in multiple invocations of bddbddb, and it is difficult to reset the state of bddbddb on each invocation. 
\end{quote}

@@

This section describes properties specifying the names of files and directories output by Chord.
Most users will not need to alter the default values of these properties.
\\[10pt]

@@

\code{chord.bddbddb.work.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory used by BDD-based Datalog solver bddbddb as its input/output directory (namely, for program domain files {\tt *.dom} and {\tt *.map}, and program relation files {\tt *.bdd}). \\
{\bf Default value:} \code{[chord.out.dir]/bddbddb/}
\end{quote}

\code{chord.boot.classes.dir}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the directory from/to which instrumented classes of the input Java program inside the JDK standard library are read/written by dynamic analyses. \\
{\bf Default value:} \code{[chord.out.dir]/boot_classes/}
\end{quote}

\code{chord.user.classes.dir}
\begin{quote}
{\bf Type:} location  \\
{\bf Description:} Absolute location of the directory from/to which instrumented classes of the input Java program outside the JDK standard library are read/written by dynamic analyses. \\
{\bf Default value:} \code{[chord.out.dir]/user_classes/}
\end{quote}

\code{chord.instr.scheme.file}
\begin{quote}
{\bf Type:} location \\
{\bf Description:} Absolute location of the file specifying the kind and format of events in trace files used by dynamic analyses. \\
{\bf Default value:} \code{[chord.out.dir]/scheme.ser}
\end{quote}

\code{chord.trace.file}
\begin{quote}
{\bf Type:} location  \\
{\bf Description:} Absolute location of trace files used by dynamic analyses. \\
{\bf Default value:} \code{[chord.out.dir]/trace} \\
{\bf Note:} Suffix \code{_full_verN.txt} or \code{_pipe_verN.txt} is appended to the name of the file, depending upon whether it is a regular file or a POSIX pipe, respectively, where {\tt N} is the version of the file (multiple versions are maintained if the trace is transformed by filters defined by the dynamic analysis; 0 is the final version).  If \code{chord.reuse.traces} is set to {\tt true}, then \code{_full_verN_runM.txt} is appended to the name of the file, where {\tt M} is the run ID. 
\end{quote}
